Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-08-30 article.tex
Minor updates

%\documentclass[sn-mathphys,Numbered]{sn-jnl}% Math and Physical Sciences Reference Style
\documentclass[sn-mathphys,Numbered,draft]{sn-jnl}% Math and Physical Sciences Reference Style

@@

\author*[1,2,3]{\fnm{Philip} \sur{Cardiff}}\email{philip.cardiff@ucd.ie}
\author[4]{\fnm{Ivan} \sur{Batisti\'{c}}}

\affil*[1]{\orgdiv{School of Mechanical and Materials Engineering}, \orgname{University College Dublin}, \orgaddress{\country{Ireland}}}
\affil[2]{\orgdiv{UCD Centre for Mechanics}, \orgname{University College Dublin}, \orgaddress{\country{Ireland}}}
\affil[3]{\orgdiv{SFI I-Form Centre}, \orgname{University College Dublin}, \orgaddress{\country{Ireland}}}
\affil[4]{\orgdiv{University of Zagreb}, \orgname{University of Zagreb}, \orgaddress{\country{Croatia}}}
%\affil[6]{\orgdiv{UCD Centre of Adhesion and Adhesives'}, \orgname{University College Dublin}, \orgaddress{\country{Ireland}}}

%Idea:
%- We need a clinical perspective: ask Peter de Jaeger. If he thinks the paper is in good shape, I could ask Emer again and/or Maryland.
%- Invite creators of CirculatorySystems Julia package.

@@

\paragraph{Case 1: Spherical Cavity in an Infinite Solid Subjected to Remote Stress}
This 3-D case consists of a spherical cavity with radius $a = 0.2$ m (Figure \ref{fig:spherical_cavity}) in an infinite, isotropic linear elastic solid ($E = 200$ GPa, $\nu = 0.3$).
Far from the cavity, the solid is subjected to a tensile stress $\sigma_{zz} = T = 1$ MPa, with all other stress components zero.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/spherical_cavity.pdf} 
   \caption{Spherical cavity case geometry, mesh and loading conditions \hl{geometry + loading conditions + maybe an example mesh. Show x/y/z axes}}
   \label{fig:spherical_cavity}
\end{figure}
The analytical expressions for the stress distributions around the cavity, first derived by \cite{Southwell1926}, are
\begin{eqnarray}
	\sigma_{rr} &=&
		\frac{T}{14 - 10\nu} \frac{a^3}{R^3}
		\left[ 9 - 15\nu - 12 \frac{a^2}{R^2}  - \frac{r^2}{R^2} \left( 72 - 15\nu - 105 \frac{a^2}{R^2} \right) + 15 \frac{r^4}{R^4} \left( 5 - 7 \frac{a^2}{R^2} \right) \right], \\
	\sigma_{\theta\theta} &=&
		\frac{T}{14 - 10\nu} \frac{a^3}{R^3}
		\left[ 9 - 15\nu - 12 \frac{a^2}{R^2}  - 15 \frac{r^2}{R^2} \left( 1 - 2\nu - \frac{a^2}{R^2} \right) \right], \\
	\sigma_{zz} &=&
		T \left[ 1 - \frac{1}{14 - 10\nu} \frac{a^3}{R^3} \left\{ 38 - 10\nu - 24 \frac{a^2}{R^2} 
		- \frac{r^2}{R^2} \left( 117 - 15\nu - 120 \frac{a^2}{R^2} \right)
		+ 15 \frac{r^4}{R^4} \left( 5 - 7 \frac{a^2}{R^2} \right) \right\} \right], \notag \\
		\\
	\sigma_{zr} &=&
	\frac{T}{14 - 10\nu} \frac{a^3 z r}{R^5}
	\left[ -3(19 - 5\nu) + 60 \frac{a^2}{R^2} + 15 \frac{r^2}{R^2} \left( 5 - 7 \frac{a^2}{R^2} \right)  \right].
\end{eqnarray}
where $r^2 = x^2 + y^2$ is the cylinderical radial coordinate, $R^2 = r^2 + z^2$ is the spherical radial coodinate, and $x$, $y$, $z$ are the Cartesian coordinates.

The solution domain is taken as one-eighth of a $1 \times 1 \times 1$ m cube centred on the sphere.
The analytical tractions are applied at the far boundaries of the domain to mitigate the effects of finite geometry.
Unstructured polyhedral meshes of varying densities are employed (\hl{state average cell widths, and number of cells in each mesh}).
A coarse mesh is shown in Figure \ref{fig:spherical_cavity}.
Initially, unstructured tetrahedral meshes were generated using the Gmsh meshing utility \cite{Gmsh}, followed by conversion to their dual polyhedral representations using the OpenFOAM \texttt{polyDualMesh} utility.

\paragraph{Case 2: Out-of-plane bending of an elliptic plate}
This 3-D, static, linear elastic test case (Figure \ref{fig:elliptic_plate}) consists of a thick elliptic plate (0.6 m thick) with a centred elliptic hole, with the inner and outer ellipses given as
\begin{eqnarray}
	\left(\frac{x}{2}\right)^2 + \left(\frac{y}{1}\right)^2 = 1 & \text{inner ellipse} \\
	\left(\frac{x}{3.25}\right)^2 + \left(\frac{y}{2.75}\right)^2 = 1 & \text{outer ellipse}
\end{eqnarray}
The case has been described by the National Agency for Finite Element Methods and Standards (NAFEMS) \cite{NAFEMS}, and analysed using finite volume procedures by \citet{Demirdzic} and \citet{Cardiff2016}.
Symmetry allows one quarter of the geometry to be simulated.
A constant pressure of 1 MPa is applied to the upper surface, and the outer surface is fully clamped.
The mechanical properties are: $E = 210$ GPa, $\nu = 0.3$.
\hl{Comment on the meshes used}.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/elliptic_plate.pdf} 
   \caption{Elliptic Plate case geometry, mesh and loading conditions}
   \label{fig:elliptic_plate}
\end{figure}

\paragraph{Case 3: Narrow T-section component under tension}
This case, proposed by \citet{Demirdzic1997}, consists of a narrow engineering component with a T cross-section (Figure \ref{fig:narrowTmember}).
The case is 3-D, static, with linear elastic material behaviour.
Symmetry allows one quarter of the geometry to be simulated.
A constant negative pressure of 1 MPa is applied to the lower surface and the upper left surface is fully clamped.
The Young’s modulus is $E = 210$ GPa and Poisson’s ratio is $\nu = 0.3$.
A hole of radius $5$ mm is located at the expected stress concentration.
\hl{Comment on the meshes}
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/narrowTmember.pdf} 
   \caption{Inflation of an idealised ventricle case geometry, mesh and loading conditions}
   \label{fig:narrowTmember}
\end{figure}

\paragraph{Case 4: Inflation of an idealised ventricle}
Inflation of an idealised ventricle (Figure \ref{fig:ventricle}) was proposed by \citet{Land2015} as a benchmark problem for cardiac mechanics software.
The case is 3-D, static, with finite hyperelastic strains.
The initial geometry is defined as a truncated ellipsoid:
\begin{eqnarray}
	x = r_s \sin(u) \cos(v), \quad
	y = r_s \sin(u) \sin(v), \quad
	z = r_l \cos(u)
\end{eqnarray}
where on the inner (endocardial) surface $r_s =7$ mm, $r_l = 17$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{17} \right) \right]$ and $v \in \left[-\pi, \pi \right]$, while on the outer (epicardial) surface $r_s =10$ mm, $r_l = 20$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{20} \right) \right]$ and $v \in \left[-\pi, \pi \right]$.
The base plane $z = 5$ mm is implicitly defined by the ranges for $u$.
%Constitutive parameters: isotropic, 
The hyperelastic material behaviour is decsribed by the transversely isotropic constitutive proposed by \citet{Guccione} law, where the parameters $C = 10$ kPa, $b_f = b_t = b_{fs} = 1$.
The chosen parameters produce isotropic behaviour.
A pressure of 10 kPa is applied to the inner surface, and the base plane is fixed.
\hl{Comment on the meshes}
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/ventricle.pdf} 
   \caption{Inflation of an idealised ventricle case geometry, mesh and loading conditions}
   \label{fig:ventricle}
\end{figure}

\paragraph{Case 5: Cook's membrane}
Cook's membrane (Figure \ref{fig:cooks_membrane}) is a well-known bending-dominated benchmark case used in linear and non-linear analysis.
In current work, the finite strain elastoplastic version \citep{Simo1992} is considered. \hl{We could also consider the small-strain elastic version if needed}
The 2-D tapered panel (trapezoid) is fixed on one side and subjected to uniform shear traction on the opposite side.
The prescribed shear traction is $\tau = 0.3125$ MPa.
The vertices of the trapezoid (in mm) are (0, 0), (48, 44), (48, 60),  and (0, 44).
There are no body forces, and the problem is solved as statically as 2-D plane strain.
The problem is solved as static, using 30 equally-sized loading increments.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/cooks_membrane.pdf} 
   \caption{Cook's membrane case geometry, mesh and loading conditions}
   \label{fig:cooks_membrane}
\end{figure}

@@

\paragraph{Case 6: Vibration of a 3-D Cantilevered Beam}
This 3-D, dynamic, finite strain case geometry consists of a $2 \times 0.2 \times 0.2$ cuboid column (Figure \ref{fig:dynamic_cantilever}), taken from \citet{Tukovic2007}.
A sudden, constant traction $\bb{T} = \left(\sfrac{|\bb{T}|}{\sqrt{2}}\right) \left(1, 1, 0 \right)$ Pa is applied to the upper surface, where the magnitude $|\bb{T}|$ is defined in terms of a dimensionless load factor $\mathcal{F}$ as
\begin{eqnarray}
	|\bb{T}| = \frac{\mathcal{F} E I}{A L^2} \text{ Pa}
\end{eqnarray}
In the current study, $\mathcal{F} = 1$.
A St.\ Venant-Kirchoff material is assumed with $E = 15.293$ MPa, $\nu = 0.3$ and density $\rho = 1000$ kg m$^{-3}$, while the area $A = (0.2)(0.2) = 0.04$ m$^2$ and the second moment of area $I = 0.0001333$ m$^4$.
The geometric and material parameters were chosen for the first natural frequency to be 1 Hz.
\hl{Comment on the meshes}
A fixed time step size of \hl{XXX} s is chosen, corresponding to a \hl{YY} on the coarsest mesh \hl{update as required}.
The total time period is 10 s, corresponding to 10 expceted oscillation periods.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/dynamic_cantilever.pdf} 
   \caption{Vibration of a 3-D Cantilevered Beam case geometry, mesh and loading conditions}
   \label{fig:dynamic_cantilever}
\end{figure}

\paragraph{Case 7: Vibration of an Axial Turbine Blade}
This 3-D, dynamic, finite strain case geometry consists of a twisted axial turbine blade, 0.8 m in height, with a cord length of 0.2 m (Figure \ref{fig:turbine_blade}), and is taken from \citet{Tukovic2007}.
\hl{Zeljko probably has this geometry or a reference for where it came from}
The blade is constrained at one end and subjected to a sudden, constant traction of $\bb{T} = ($\hl{ZZZ,ZZZ,ZZZ} $)$ Pa at the other end.
A St.\ Venant-Kirchoff material is assumed with $E = 15.293$ MPa and $\nu = 0.3$, while the area $A = (0.2)(0.2) = 0.04$ m$^2$ and the second moment of area $I = 0.0001333$ m$^4$.
\hl{Comment on the meshes}
A fixed time step size of \hl{XXX} s is chosen, corresponding to a \hl{YY} on the coarsest mesh \hl{update as required}.
The total time period is \hl{XXX} s, corresponding to \hl{XX} expceted oscillation periods.
\hl{An advantage of this case over the cantilever is that it is complex geometry; a disadvantage is that we do not have a reference solution}
\hl{A mitigation for this disadvantage is we could run it in Abaqus to provide a credible reference}
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/turbine_blade.pdf} 
   \caption{Vibration of an axial turbine blade case geometry, mesh and loading conditions}
   \label{fig:turbine_blade}
\end{figure}

@@

The predicted axial ($\sigma_{zz}$) stress distribution is shown in Figure \ref{fig:spherical_cavity_stress}, where the peak stress ($2.xxx$ MPa) is just over twice the applied stress ($1$ MPa).
This is in contrast to the classic 2-D circular hole in an infinite plate case, which exhibits a stress concentration factor of 3.
A further difference with the 2-D circular hole case is that the local stresses more quickly return to the distant stress state as $R$ increases, with the local stresses being proportional to $\frac{1}{R^3}$ in the 3-D case and  $\frac{1}{R^2}$ in the 2-D case.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/spherical_cavity_stress.pdf} 
   \caption{Spherical cavity case: $\sigma_{zz}$ stress distribution \hl{use Reflect in ParaView to make a nice image}}
   \label{fig:spherical_cavity_stress}
\end{figure}

Figure \ref{fig:spherical_cavity_accuracy} shows the discretisation errors ($L_2$ and $L_\infty$) in $\sigma_{zz}$ as a function of the average cell width.
The errors can be seen to \hl{describe on the average/max error trends in graphs}.
\hl{Comment on the order of accuracy: does it show what was expected or not?}
\hl{Conclude 1: order of accuracy of the discretisation is XXX}
\hl{Conclude 2: solution algorithm does not affect the answer}
\hl{There is no need to show segregated results if they are the same: just state that they are the same}
\hl{There is no need to show time and memory requirements: leave to the next section}
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/spherical_cavity_error.pdf} 
   \caption{Spherical cavity case: discretisation error as a function of average cell width \hl{disp and stress errors if we have them}}
   \label{fig:spherical_cavity_accuracy}
\end{figure}

@@

Figure \ref{fig:time_memory_images} provides a collage of the equivalent (von Mises) stress fields for the \hl{six} cases.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/time_memory_images.pdf} 
   \caption{Collage of the equivalent (von Mises) stress fields for the \hl{six} cases}
   \label{fig:time_memory_images}
\end{figure}

@@

Figure \ref{fig:rhie_chow} shows a comparison of the stress \hl{(or displacement)} along the line \hl{XXX -> we need to show the effect on accuracy for different values of alpha}
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/rhie_chow.pdf} 
   \caption{Stress predictions along the line \hl{XXX} for the \hl{YYY} case using different values of the Rhie-Chow stabilisation factor $\alpha$}
   \label{fig:rhie_chow}
\end{figure}

@@

The results from the strong scaling study are shown in Figure \ref{fig:parallelisation_strong}.
The speedup $S$ is defined as $S = \sfrac{t_1}{t_p}$, where $t_1$ is the clock time on one CPU core and $t_p$ is the clock time on $P$ CPU cores.
In the ideal case, the speedup should double when the number of cores is doubled.
In reality, inter-CPU-core communication reduces the parallel scaling efficiency below the ideal.
\hl{Comment on the results: e.g. fastest, slowest, most/least iterations, best/worst scaling}
\hl{Provide insights, if any: e.g. why is one faster or slower}
\begin{figure}[htbp]
	\centering
	\subfigure[Clock times vs number of CPU cores] {\label{fig:parallel_strong_times} \includegraphics[width=0.2\textwidth]{./figures/parallel_strong_times.pdf}}
	\subfigure[Speedup $S$ vs number of CPU cores] {\label{fig:parallel_strong_speedup} \includegraphics[width=0.2\textwidth]{./figures/parallel_strong_speedup.pdf}}
	\caption{Strong parallel scaling study comparing the performance of three preconditioning strategies: a LU direct solver, and ILU(N) and multigrid iterative solvers}
	\label{fig:parallelisation_strong}
\end{figure}

>>>>

\documentclass[sn-mathphys,Numbered]{sn-jnl}% Math and Physical Sciences Reference Style
%\documentclass[sn-mathphys,Numbered,draft]{sn-jnl}% Math and Physical Sciences Reference Style

@@

\author*[1,2,3]{\fnm{Philip} \sur{Cardiff}}\email{philip.cardiff@ucd.ie}
\author[4]{\fnm{Ivan} \sur{Batisti\'{c}}}
\author[4]{\fnm{\v{Z}eljko} \sur{Tukovi\'{c}}}

\affil*[1]{\orgdiv{School of Mechanical and Materials Engineering}, \orgname{University College Dublin}, \orgaddress{\country{Ireland}}}
\affil[2]{\orgdiv{UCD Centre for Mechanics}, \orgname{University College Dublin}, \orgaddress{\country{Ireland}}}
\affil[3]{\orgdiv{SFI I-Form Centre}, \orgname{University College Dublin}, \orgaddress{\country{Ireland}}}
\affil[4]{\orgdiv{University of Zagreb}, \orgname{University of Zagreb}, \orgaddress{\country{Croatia}}}

@@

\paragraph{Case 1: Spherical Cavity in an Infinite Solid Subjected to Remote Stress}
This 3-D case consists of a spherical cavity with radius $a = 0.2$ m (Figure \ref{fig:spherical_cavity}) in an infinite, isotropic linear elastic solid ($E = 200$ GPa, $\nu = 0.3$).
Far from the cavity, the solid is subjected to a tensile stress $\sigma_{zz} = T = 1$ MPa, with all other stress components zero.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.4\textwidth]{figures/spherical_cavity.pdf} 
   \caption{Spherical cavity case geometry, showing the polyhedral mesh with 2,257 cells \hl{Update to graded mesh}}
   \label{fig:spherical_cavity}
\end{figure}
The analytical expressions for the stress distributions around the cavity, first derived by \cite{Southwell1926}, are
\begin{eqnarray}
	\sigma_{rr} &=&
		\frac{T}{14 - 10\nu} \frac{a^3}{R^3}
		\left[ 9 - 15\nu - 12 \frac{a^2}{R^2}  - \frac{r^2}{R^2} \left( 72 - 15\nu - 105 \frac{a^2}{R^2} \right) + 15 \frac{r^4}{R^4} \left( 5 - 7 \frac{a^2}{R^2} \right) \right], \\
	\sigma_{\theta\theta} &=&
		\frac{T}{14 - 10\nu} \frac{a^3}{R^3}
		\left[ 9 - 15\nu - 12 \frac{a^2}{R^2}  - 15 \frac{r^2}{R^2} \left( 1 - 2\nu - \frac{a^2}{R^2} \right) \right], \\
	\sigma_{zz} &=&
		T \left[ 1 - \frac{1}{14 - 10\nu} \frac{a^3}{R^3} \left\{ 38 - 10\nu - 24 \frac{a^2}{R^2} 
		- \frac{r^2}{R^2} \left( 117 - 15\nu - 120 \frac{a^2}{R^2} \right)
		+ 15 \frac{r^4}{R^4} \left( 5 - 7 \frac{a^2}{R^2} \right) \right\} \right], \notag \\
		\\
	\sigma_{zr} &=&
	\frac{T}{14 - 10\nu} \frac{a^3 z r}{R^5}
	\left[ -3(19 - 5\nu) + 60 \frac{a^2}{R^2} + 15 \frac{r^2}{R^2} \left( 5 - 7 \frac{a^2}{R^2} \right)  \right].
\end{eqnarray}
where $r^2 = x^2 + y^2$ is the cylinderical radial coordinate, $R^2 = r^2 + z^2$ is the spherical radial coodinate, and $x$, $y$, $z$ are the Cartesian coordinates.

\hl{Add displacement equations from Goodier}
\hl{We can move the analytical solutions to an appendix}

The solution domain is taken as one-eighth of a $1 \times 1 \times 1$ m cube centred on the sphere.
The analytical tractions are applied at the far boundaries of the domain to mitigate the effects of finite geometry.
Unstructured polyhedral meshes of varying densities are employed (\hl{state average cell widths, and number of cells in each mesh}).
The mesh with 2,257 cells is shown in Figure \ref{fig:spherical_cavity}.
Initially, unstructured tetrahedral meshes were generated using the Gmsh meshing utility \cite{Gmsh}, followed by conversion to their dual polyhedral representations using the OpenFOAM \texttt{polyDualMesh} utility.

\paragraph{Case 2: Out-of-plane bending of an elliptic plate}
This 3-D, static, linear elastic test case (Figure \ref{fig:elliptic_plate}) consists of a thick elliptic plate (0.6 m thick) with a centred elliptic hole, with the inner and outer ellipses given as
\begin{eqnarray}
	\left(\frac{x}{2}\right)^2 + \left(\frac{y}{1}\right)^2 = 1 & \text{inner ellipse} \\
	\left(\frac{x}{3.25}\right)^2 + \left(\frac{y}{2.75}\right)^2 = 1 & \text{outer ellipse}
\end{eqnarray}
The case has been described by the National Agency for Finite Element Methods and Standards (NAFEMS) \cite{NAFEMS}, and analysed using finite volume procedures by \citet{Demirdzic} and \citet{Cardiff2016}.
Symmetry allows one quarter of the geometry to be simulated.
A constant pressure of 1 MPa is applied to the upper surface, and the outer surface is fully clamped.
The mechanical properties are: $E = 210$ GPa, $\nu = 0.3$.
\hl{Comment on the meshes used}.
\begin{figure}[htbp]
   \centering
   %\includegraphics[width=0.2\textwidth]{figures/elliptic_plate.pdf} 
   \includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   \caption{Elliptic Plate case geometry, mesh and loading conditions}
   \label{fig:elliptic_plate}
\end{figure}

\paragraph{Case 3: Narrow T-section component under tension}
This case, proposed by \citet{Demirdzic1997}, consists of a narrow engineering component with a T cross-section (Figure \ref{fig:narrowTmember}).
The case is 3-D, static, with linear elastic material behaviour.
Symmetry allows one quarter of the geometry to be simulated.
A constant negative pressure of 1 MPa is applied to the lower surface and the upper left surface is fully clamped.
The Young’s modulus is $E = 210$ GPa and Poisson’s ratio is $\nu = 0.3$.
A hole of radius $5$ mm is located at the expected stress concentration.
\hl{Comment on the meshes}
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.2\textwidth]{figures/narrowTmember.pdf} 
   \includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   \caption{Inflation of an idealised ventricle case geometry, mesh and loading conditions}
   \label{fig:narrowTmember}
\end{figure}

\paragraph{Case 4: Inflation of an idealised ventricle}
Inflation of an idealised ventricle (Figure \ref{fig:ventricle}) was proposed by \citet{Land2015} as a benchmark problem for cardiac mechanics software.
The case is 3-D, static, with finite hyperelastic strains.
The initial geometry is defined as a truncated ellipsoid:
\begin{eqnarray}
	x = r_s \sin(u) \cos(v), \quad
	y = r_s \sin(u) \sin(v), \quad
	z = r_l \cos(u)
\end{eqnarray}
where on the inner (endocardial) surface $r_s =7$ mm, $r_l = 17$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{17} \right) \right]$ and $v \in \left[-\pi, \pi \right]$, while on the outer (epicardial) surface $r_s =10$ mm, $r_l = 20$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{20} \right) \right]$ and $v \in \left[-\pi, \pi \right]$.
The base plane $z = 5$ mm is implicitly defined by the ranges for $u$.
%Constitutive parameters: isotropic, 
The hyperelastic material behaviour is decsribed by the transversely isotropic constitutive proposed by \citet{Guccione} law, where the parameters $C = 10$ kPa, $b_f = b_t = b_{fs} = 1$.
The chosen parameters produce isotropic behaviour.
A pressure of 10 kPa is applied to the inner surface, and the base plane is fixed.
The geometry is meshed using structured approach and is predominantly composed of hexahedra, with prism cells forming the apex.
Four succesively refined meshes are examined: 1,620 (shown in Figure  \ref{fig:ventricle}), 12,960, 103,680, and 829,440 cells.
%Figure \ref{fig:ventricle} shows the mesh with 1,620 cells (1,512 hexahedra and 108 prisms).
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.4\textwidth]{figures/ventricle} 
   \caption{Idealised ventricle case geometry, showing the mesh with 1,620 cells}
   \label{fig:ventricle}
\end{figure}

\paragraph{Case 5: Cook's membrane}
Cook's membrane (Figure \ref{fig:cooks_membrane}) is a well-known bending-dominated benchmark case used in linear and non-linear analysis.
In current work, the finite strain elastoplastic version \citep{Simo1992} is considered. \hl{We could also consider the small-strain elastic version if needed}
The 2-D tapered panel (trapezoid) is fixed on one side and subjected to uniform shear traction on the opposite side.
The prescribed shear traction is $\tau = 0.3125$ MPa.
The vertices of the trapezoid (in mm) are (0, 0), (48, 44), (48, 60),  and (0, 44).
There are no body forces, and the problem is solved as statically as 2-D plane strain.
The problem is solved as static, using 30 equally-sized loading increments.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.4\textwidth]{figures/cooksMembrane-geometry.png} 
   \caption{Cook's membrane case geometry (dimensions in mm) and loading conditions (fixed left, traction $\tau$ applied to right)}
   \label{fig:cooks_membrane}
\end{figure}

@@

\paragraph{Case 6: Vibration of a 3-D Cantilevered Beam}
This 3-D, dynamic, finite strain case geometry consists of a $2 \times 0.2 \times 0.2$ cuboid column (Figure \ref{fig:dynamic_cantilever}), taken from \citet{Tukovic2007}.
A sudden, constant traction $\bb{T} = \left(\sfrac{|\bb{T}|}{\sqrt{2}}\right) \left(1, 1, 0 \right)$ Pa is applied to the upper surface, where the magnitude $|\bb{T}|$ is defined in terms of a dimensionless load factor $\mathcal{F}$ as
\begin{eqnarray}
	|\bb{T}| = \frac{\mathcal{F} E I}{A L^2} \text{ Pa}
\end{eqnarray}
In the current study, $\mathcal{F} = 1$.
A St.\ Venant-Kirchoff material is assumed with $E = 15.293$ MPa, $\nu = 0.3$ and density $\rho = 1000$ kg m$^{-3}$, while the area $A = (0.2)(0.2) = 0.04$ m$^2$ and the second moment of area $I = 0.0001333$ m$^4$.
The geometric and material parameters were chosen for the first natural frequency to be 1 Hz.
\hl{Comment on the meshes}
A fixed time step size of \hl{XXX} s is chosen, corresponding to a \hl{YY} on the coarsest mesh \hl{update as required}.
The total time period is 10 s, corresponding to 10 expceted oscillation periods.
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.2\textwidth]{figures/dynamic_cantilever.pdf} 
   \includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   \caption{Vibration of a 3-D Cantilevered Beam case geometry, mesh and loading conditions}
   \label{fig:dynamic_cantilever}
\end{figure}

\paragraph{Case 7: Vibration of an Axial Turbine Blade}
This 3-D, dynamic, finite strain case geometry consists of a twisted axial turbine blade, 0.8 m in height, with a cord length of 0.2 m (Figure \ref{fig:turbine_blade}), and is taken from \citet{Tukovic2007}.
\hl{Zeljko probably has this geometry or a reference for where it came from}
The blade is constrained at one end and subjected to a sudden, constant traction of $\bb{T} = ($\hl{ZZZ,ZZZ,ZZZ} $)$ Pa at the other end.
A St.\ Venant-Kirchoff material is assumed with $E = 15.293$ MPa and $\nu = 0.3$, while the area $A = (0.2)(0.2) = 0.04$ m$^2$ and the second moment of area $I = 0.0001333$ m$^4$.
\hl{Comment on the meshes}
A fixed time step size of \hl{XXX} s is chosen, corresponding to a \hl{YY} on the coarsest mesh \hl{update as required}.
The total time period is \hl{XXX} s, corresponding to \hl{XX} expceted oscillation periods.
\hl{An advantage of this case over the cantilever is that it is complex geometry; a disadvantage is that we do not have a reference solution}
\hl{A mitigation for this disadvantage is we could run it in Abaqus to provide a credible reference}
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.2\textwidth]{figures/turbine_blade.pdf} 
   \includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   \caption{Vibration of an axial turbine blade case geometry, mesh and loading conditions}
   \label{fig:turbine_blade}
\end{figure}

@@

The predicted axial ($\sigma_{zz}$) stress distribution is shown in Figure \ref{fig:spherical_cavity_stress}, where the peak stress ($2.xxx$ MPa) is just over twice the applied stress ($1$ MPa).
This is in contrast to the classic 2-D circular hole in an infinite plate case, which exhibits a stress concentration factor of 3.
A further difference with the 2-D circular hole case is that the local stresses more quickly return to the distant stress state as $R$ increases, with the local stresses being proportional to $\frac{1}{R^3}$ in the 3-D case and  $\frac{1}{R^2}$ in the 2-D case.
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.2\textwidth]{figures/spherical_cavity_stress.pdf} 
   \includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   \caption{Spherical cavity case: $\sigma_{zz}$ stress distribution \hl{use Reflect in ParaView to make a nice image}}
   \label{fig:spherical_cavity_stress}
\end{figure}

Figure \ref{fig:spherical_cavity_accuracy} shows the discretisation errors ($L_2$ and $L_\infty$) in $\sigma_{zz}$ as a function of the average cell width.
The errors can be seen to \hl{describe on the average/max error trends in graphs}.
\hl{Comment on the order of accuracy: does it show what was expected or not?}
\hl{Conclude 1: order of accuracy of the discretisation is XXX}
\hl{Conclude 2: solution algorithm does not affect the answer}
\hl{There is no need to show segregated results if they are the same: just state that they are the same}
\hl{There is no need to show time and memory requirements: leave to the next section}
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.2\textwidth]{figures/spherical_cavity_error.pdf} 
   \includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   \caption{Spherical cavity case: discretisation error as a function of average cell width \hl{disp and stress errors if we have them}}
   \label{fig:spherical_cavity_accuracy}
\end{figure}

@@

Figure \ref{fig:time_memory_images} provides a collage of the equivalent (von Mises) stress fields for the \hl{six} cases.
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.2\textwidth]{figures/time_memory_images.pdf} 
   \includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   \caption{Collage of the equivalent (von Mises) stress fields for the \hl{six} cases}
   \label{fig:time_memory_images}
\end{figure}

@@

Figure \ref{fig:rhie_chow} shows a comparison of the stress \hl{(or displacement)} along the line \hl{XXX -> we need to show the effect on accuracy for different values of alpha}
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.2\textwidth]{figures/rhie_chow.pdf} 
   \includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   \caption{Stress predictions along the line \hl{XXX} for the \hl{YYY} case using different values of the Rhie-Chow stabilisation factor $\alpha$}
   \label{fig:rhie_chow}
\end{figure}

@@

The results from the strong scaling study are shown in Figure \ref{fig:parallelisation_strong}.
The speedup $S$ is defined as $S = \sfrac{t_1}{t_p}$, where $t_1$ is the clock time on one CPU core and $t_p$ is the clock time on $P$ CPU cores.
In the ideal case, the speedup should double when the number of cores is doubled.
In reality, inter-CPU-core communication reduces the parallel scaling efficiency below the ideal.
\hl{Comment on the results: e.g. fastest, slowest, most/least iterations, best/worst scaling}
\hl{Provide insights, if any: e.g. why is one faster or slower}
\begin{figure}[htbp]
	\centering
	\subfigure[Clock times vs number of CPU cores]
	{
		\label{fig:parallel_strong_times}
%		\includegraphics[width=0.2\textwidth]{./figures/parallel_strong_times.pdf}
   		\includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   	}
	\subfigure[Speedup $S$ vs number of CPU cores]
	{
		\label{fig:parallel_strong_speedup}
%		\includegraphics[width=0.2\textwidth]{./figures/parallel_strong_speedup.pdf}
   		\includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   	}
	\caption{Strong parallel scaling study comparing the performance of three preconditioning strategies: a LU direct solver, and ILU(N) and multigrid iterative solvers}
	\label{fig:parallelisation_strong}
\end{figure}

The weak scaling results are shown in Figure \ref{fig:parallelisation_weak}.
The weak scaling efficiency $\eta_w$ is defined as $\eta_w = \sfrac{t^[w]_1}{t^[w]_p}$, where $t^[w]_1$ is the clock time on one CPU core and $t^[w]_p$ is the clock time on $P$ CPU cores where the problem size per CPU core is constant.
In the ideal case, the efficiency should be unity, but inter-CPU-core communication reduces it.
\hl{Comment on the results: e.g. fastest, slowest, most/least iterations, best/worst scaling}
\hl{Provide insights, if any: e.g. why is one faster or slower}
\begin{figure}[htbp]
	\centering
	\subfigure[Clock times vs number of CPU cores]
	{
		\label{fig:parallel_weak_times}
%		\includegraphics[width=0.2\textwidth]{./figures/parallel_weak_times.pdf}
   		\includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   	}
	\subfigure[Weak scaling efficiency $\eta_w$ vs number of CPU cores]
	{
		\label{fig:parallel_weak_speedup}
%		\includegraphics[width=0.2\textwidth]{./figures/parallel_weak_efficiency.pdf}
   		\includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   	}
	\caption{Weak parallel scaling study comparing the performance of three preconditioning strategies: a LU direct solver, and ILU(N) and multigrid iterative solvers}
	\label{fig:parallelisation_weak}
\end{figure}
